### 2020-02-04 Common/chapters/literature_review.tex
Johan and Julien: continue literature review

Computer-aided cancer detection is a trending topic in deep learning. Nowadays, articles tend to focus more on segmentation than classification, but classification still got a lot of attention over the last decade.

\section{Prostate/PROSTATEx}
PROSTATEx: section \ref{sec:PROSTATEx}.

@@

\section{Lung/Lung CT Challenge}
SPIE-AAPM Lung CT Challenge is lung cancer classification dataset. It is described in detail in section \ref{sec:lungCTChallenge}.

>>>>

Traditionally building a computer-aider cancer diagnosis or detection (CAD) system consisted in two different parts: "Lesion  detection  and  false-positive  reduction.  Lesion  detection  was  primarily  based  on  algorithms  specific  to  the  detection task, resulting in many candidate lesions. False-positive reduction was commonly based on traditional  machine  learning  methods  to  reduce  the  false  positive  rate. However,  even  with  these  complicated and sophisticated programs, the general performance of conventional CAD systems was not good, thus hampering their widespread usage in clinical practice"\cite{41}.\\
Nowadays, this two steps tend to disappear thanks to deep learning algorithms, in particular the one based on convolutional neural networks, that constitute themselves CAD of one single step. This is the reason why CAD systems are currently a trending topic in deep learning.\\
There mainly exists two types of CAD systems based on convolutional neural networks. The first one is called CADe for "computer-aided detection". Their primary goal is "to increase the detection rate of diseases while reducing the false negative  rate  possibly  due  to  the  observers’  mistakes  or  fatigue"\cite{41}. This group includes medical  image  analysis  tasks  such  as  segmentation,  identification,  localization  and  detection. The other type is CADx for "computer-aided diagnosis" that aim to characterize the lesions.\\
Consequently, this chapter will go through the main articles about CADe systems using convolutional neural networks for each body part used in the experiment of section \ref{ch:transfer_learning} and \ref{ch:paper_reproduction}, that are prostate, lung and brain.

\section{Prostate/PROSTATEx}
"Prostate  cancer  is  the  most  common  malignancies  among  men  and  remains  a  second  leading  cause to deaths in men globally. It was predicted that there would be 1.7 million new cancer cases by 2030. The early detection and diagnosis of prostate cancer can help to survive nine out of 10 men for the last five years"\cite{41}.
PROSTATEx: section \ref{sec:PROSTATEx}.

@@

\section{Lung/Lung CT Challenge}
"Lung cancer is one of the most frequent and leading causes to death all over the world. It was reported that there were approximately 1.8x106 new cases of lung cancer globally in 2012. Early detection of lung cancer, which is typically viewed in the form of lung nodules, is an efficient way to improve the survival rate"\cite{41}.
SPIE-AAPM Lung CT Challenge is lung cancer classification dataset. It is described in detail in section \ref{sec:lungCTChallenge}.
